Stack Safety as a Security Property

### 2020-07-09 main.tex
Read 4, added pointers to policy intro and example

A policy is a general model of an enforcement mechanism, consisting of a
set of policy states \(\pol \in \POLS\), a policy step function
\((\mach, \pol) \polstep \pol' : \MACHS \times \POLS
\rightharpoonup \POLS\), and an initializer \(\pinit : \MACHS \rightharpoonup
\POLS\). The initializer establishes the initial policy state for a given
machine state, but is partial to reflect that some policies are only defined
on states that are well-formed in some way.\apt{Is this our current thinking?}

@@

\apt{TODO: relate back to \Cref{sec:threat} and forward to \Cref{sec:enforcement}.}
%\leo{TODO: Forward pointer to policies right?}\bcp{Yes.  But also we can say
%in more detail that the intention is to capture any kind of dynamic
%enforcement mechanism and give as many names and citations as we can.}

>>>>

We now present our model of enforcement, introduced informally in \Cref{sec:threat}.
A policy is a general model of an enforcement mechanism, consisting of a
set of policy states \(\pol \in \POLS\), a policy step function
\((\mach, \pol) \polstep \pol' : \MACHS \times \POLS
\rightharpoonup \POLS\), and an initializer \(\pinit : \MACHS \rightharpoonup
\POLS\). The initializer establishes the initial policy state for a given
machine state, but is partial to reflect that some policies are only defined
on states that are well-formed in some way.\apt{Is this our current thinking?}

@@

A concrete policy based on \citet{DBLP:conf/sp/RoesslerD18} will be given in
\Cref{sec:enforcement}.

\apt{TODO: relate back to \Cref{sec:threat} and forward to \Cref{sec:enforcement}.}
\rb{Added some quick pointers, although one might expect to see Nick's policy
as a more formal instance of this framework, which at the moment it is not.}

%\leo{TODO: Forward pointer to policies right?}\bcp{Yes.  But also we can say
%in more detail that the intention is to capture any kind of dynamic
%enforcement mechanism and give as many names and citations as we can.}
